### 2016-09-10 draft/draft.tex
Add bibtex meta directives

\documentclass[]{article}

@@

{
\setcounter{tocdepth}{3}
\tableofcontents
}
\#\#

@@

@@

Working from this technological and philosophical objective,
respectively, the following goals were established for the project: -
Create a public Application Programming Interface (henceforth API) to
allow users to interact with a blockchain in a well-defined manner,
independent of a chosen client-side implementation. - Provide an iOS
client-side app for basic task/user/team management to offer a graphical
representation of the API in a format familiar to users. - Establish a
basic deployment of at least 4 distributed validator nodes to implement
a true proof-of-stake consensus
mechanism\href{http://bitfury.com/content/5-white-papers-research/pos-vs-pow-1.0.2.pdf}{PoW
vs PoS} for the platform.

>>>>

\documentclass[12pt]{report}

\usepackage[
backend=biber,
style=ieee,
sorting=ynt
]{biblatex}

\addbibresource{main.bib}

\usepackage{titlesec}
\usepackage{listings}
\usepackage{booktabs}
\usepackage[normalem]{ulem}
\useunder{\uline}{\ul}{}
\titleformat{\chapter}[display]
{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter}{10pt}{\Huge}
\titlespacing*{\chapter}{0pt}{-70pt}{15pt}

\renewcommand{\baselinestretch}{1.5}
\lstset{breaklines=true}

@@

\#\#

@@

{
\setcounter{tocdepth}{3}
\tableofcontents
}

@@

Working from this technological and philosophical objective,
respectively, the following goals were established for the project: -
Create a public Application Programming Interface (henceforth API) to
allow users to interact with a blockchain in a well-defined manner,
independent of a chosen client-side implementation. - Provide an iOS
client-side app for basic task/user/team management to offer a graphical
representation of the API in a format familiar to users. - Establish a
basic deployment of at least 4 distributed validator nodes to implement
a true proof-of-stake consensus
mechanism\cite{BitFuryGroup2015} for the platform.
